\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-23 papers/jss/article.Rnw
Improve the typesetting for the section 5 type coercion examples.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@824 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

<<>>=
a <- new(protobuf_unittest.TestAllTypes)
a$optional_bool <- TRUE
a$optional_bool <- FALSE
<<eval=FALSE>>=
a$optional_bool <- NA
<<echo=FALSE,eval=TRUE,print=TRUE>>=
try(a$optional_bool <- NA,silent=TRUE)
@

@@

<<>>=
as.integer(2^31-1)
<<eval=FALSE>>=
as.integer(2^31 - 1) + as.integer(1)
<<echo=FALSE,eval=TRUE,print=TRUE>>=
try(as.integer(2^31 - 1) + as.integer(1))

2^31
class(2^31)
@

>>>>

% We want a cleaner error message here.
\begin{CodeChunk}
\begin{CodeInput}
R> a <- new(protobuf_unittest.TestAllTypes)
R> a$optional_bool <- TRUE
R> a$optional_bool <- FALSE
R> a$optional_bool <- NA
\end{CodeInput}
\begin{CodeOutput}
Error: NA boolean values can not be stored in bool protocol buffer fields
\end{CodeOutput}
\end{CodeChunk}

@@

<<>>=
as.integer(2^31-1)
as.integer(2^31 - 1) + as.integer(1)
2^31
class(2^31)
@
